---
title: "radiation_analysis"
author: "Lily Diao"
date: "4/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(lubridate)
library(ggplot2)
library(dplyr)
library(png)
library(grid)
library(rgdal)
library(raster)
library(sp)
library(spdep)
```

```{r}
# files and image
mobile<-read.csv("MobileSensorReadings.csv")
static<-read.csv("StaticSensorReadings.csv")
image<-readPNG("StHimarkNeighborhoodMap.png")
image_raster<-rasterGrob(image, interpolate=TRUE)
#View(static)
```



# Changes in Mobile Radiation Recording Overtime

Our initial goal with radiation data is to identify the period of time where there is an increase in radiation as well as the location being affected.

## Number of Mobile Recordings of Radiation Versus Time 04-06 to 04-10

We started off by oberving the changes the mobile radiation detection. We found that the recordings of the personally owned radiation app have the largest volume from 04-06 to 04-08's morning. Flutuations was observed from 04-08 to 04-10. This could correspond to scientists and other citizen's responds to the severity of the earth quake and subsequent leakage.
```{r}
mobile_by_second<-mobile %>% 
  group_by(Timestamp) %>% 
  summarise(count=n())
```

```{r}
time_mobile_second <- mobile_by_second %>%
  plot_ly(x = ~Timestamp, y = ~count) %>%
  add_lines(alpha = 0.4) 
time_mobile_second
```

## The Value of Radiation Versus Time

We then looked at the change in radiation level. The change in radiation values through time shows that there is an extremely large surge in radiation on at 02:43:25 on 04-09, with a measurement of 57.3452k cpm. Normal range of radiation should be between 30-50 cpm (https://ehs.iupui.edu/doc/rad/RST%20-%20geiger%20counters%205-00.pdf).
```{r}
time_mobile_value <- mobile %>%
  plot_ly(x = ~Timestamp, y = ~Value) %>%
  add_lines(alpha = 0.4) 
time_mobile_value
```

However, other recordings aside of the extreme value are also out of the normal range. So we removed the outlier and report the value of radiation with time. We noticed that starting from 04-06, the radiation level was higher than the recommended value, and from the evening of 04-09 to the morning of 04-10, the radiation level was high for a constant period of time. 

```{r}
mobile_no_outlier<-mobile %>% 
  filter(Value<50000)
```

```{r}
time_mobile_value_2 <- mobile_no_outlier %>%
  plot_ly(x = ~Timestamp, y = ~Value) %>%
  add_lines(alpha = 0.4) 
time_mobile_value_2
```



# Locations of Large Amount of Radiation Detected

We want to understand where is the largest radiation detected, as well as the large amount of radiation detected from 04-09 to 04-10.
```{r}
#subsizing the mobile data
mobile_largest<-mobile %>% 
  filter(Value>50000)
```

We saw that the site with the greatest radiation detected was at West Parton, which is not that close to the center of radiation. 
```{r}
#plotting mobile data with map
mobile_map<-ggplot(mobile_largest, aes(x=Long, y=Lat))+
  annotation_custom(rasterGrob(image, width = unit(1, "npc"), height= unit(1, "npc")))+
  geom_point(fill="blue", size=3, shape=23)
mobile_map
```

```{r}
#mobile_inereased_radiation<-mobile %>% 
  #filter(as.POSIXct(Timestamp)>= as.POSIXct('2020-04-09 19:24:00') & as.POSIXct(Timestamp) <= as.POSIXct('2020-04-09 23:59:00'))
```

```{r}
mobile_largest_radiation<-mobile %>% 
  filter(Value>2000)
```

geom_point(fill="blue", size=3, shape=23
annotation_custom(image_raster, xmin=-119.9076, xmax=-119.8150, ymin=0.054810, ymax=0.210250)
```{r}
#plotting mobile data with map, largest datapoints
mobile_map_largest<-ggplot(mobile_largest_radiation, aes(x=Long, y=Lat))+
  annotation_custom(image_raster)+
  geom_point()+
  geom_jitter(width=0.005, height = 0.005)+
  coord_fixed()
  
ggplotly(mobile_map_largest)

```

```{r}
# reading shape files
#shp<-readOGR(dsn='.', layer="StHimark.shp")
```

```{r}
read_sf("~/Documents/CSC 235/dc-5/StHimark.shp")
```


```{r}
#shape<-readOGR(dsn = ".", layer = "StHimark")
```

